Astr 513: Final Project

### 2016-05-05 Final_Project/ms.tex
Wrote likelihood. Fixed figure captions. Put in line breaks. Added an appendix.

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/corner_example.eps}
  \caption{Example corner plot.}
  \label{fig:corner}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/corner_example.eps}
  \caption{\TM{THIS IS A PLACE HOLDER PLOT!}
    Posterior distributions of the cosmological parameters in the
    analysis of the \citet{Betoule2014} data. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:corner}
\end{figure}

@@

\appendix
\section{Posterior Distribution Functions Without \Planck Priors}
\TM{Since there are potentially a bunch of corner plots, we could jam a bunch of
  them here as well as perhaps the discussion of what happens when we remove
  the priros. Let me know your thoughts.}
